LHC abort gap monitor electronics upgrade

### 2024-04-22 paper.tex
added new bibtexs and working principle finished

\subsection{Working principle}
The SL spectrum at the flat-top energy \SI{6.8}{TeV} is in visible band, which
is measured by a optical front-end. This consists of MCP-PMT,
converting SL to electric current, filters, and pre-amplifier to increase
magnitude before sending the signal \SI{100}{m} far away data acquisition
system (DAQ). The PMT is gate, that it opens just at the moment of abort gap. 
\\
When SL is converted it is amplified and send to the DAQ. The system is
synchronous with the RF timing, that it gets information about bunch position
and turn start. The signal goes to through amplifier to the integrator, where
it is decimated by factor 10. The system is gated. Its measure window is
\SI{6.4}{\micro\second} long, but the gate opens just for the time of the abort
gap. The decimate the data to \SI{100}{ns} sample period. In other words system
measures 64 values, but just 30 have valid value. Each of these values goes to
the Exponential moving averager. This type of filter has a feedback, so the
its output reflects the evolution of the charge in the abort gap.

>>>>

\subsection{Working principle}

The measurement period is determined by the MCP-PMT used, which is the gated
HAMAMATSU R5916U-50 with a duty cycle of \SI{1}{\%}. With a gate pulse duration
of \SI{3}{\micro\second} and one turn cycle length of \SI{89}{\micro\second},
measurements are taken every 4th clock cycle (\SI{356}{\micro\second}),
reducing the duty cycle to \SI{0.84}{\%}.\\
The system captures 64 values with a granularity of \SI{100}{\nano\second}. The
MCP-PMT gate duration is \SI{3}{\micro\second} providing an additional degree of
freedom in system control. The data undergo exponential moving
averaging and are provided to the software every \SI{100}{\micro\second}. Due to
variatous particle effects, the time taken to populate the AG ranges from
\SI{1.6}{\second} to \SI{25}{\second}~\cite{high_sensitivity_measurement}.
